A survey of HTTP caching options on the open Web

### 2015-01-12 sanity/paper1.tex
conditionals
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@961 43ef1190-90fd-4dd7-a769-d0121f02b80e

\subsubsection{Simple heuristic freshness estimates}

@@

>>>>

\subsubsection{Simple heuristic freshness estimates}\label{sec:simplefresh}

@@

The BTC had recorded these headers in their data, where 1733 had the
\httph{ETag} header and 690 had \httph{Last-Modified} with a great
overlap. For the resources where either or both were available, we
made our initial request conditional, and 911 responses were verified
as still fresh.

In total, 1260 successful initial responses contained
an \httph{ETag}, 606 for vocabularies, 117 for datasets, just 12 for
endpoints and 525 for unclassified information resources.

To see if the server actually supported conditional requests, and not
just merely set the response headers, we made another 1822 requests to
the resources that had these headers. Then, we checked if the response
code was 200, and the conditional headers had not changed since our
initial requests. In 85 cases, conditional requests were not supported
according to the standard, no cases for endpoints, 3 for datasets and
23 for vocabularies, 59 for generic information resources.\todo{table instead?}

We already used \httph{Last-Modified} to compute heuristic lifetime
in Section~\ref{sec:simplefresh} for 554 resources.\todo{really needed?}
